Cropland Bias and Accuracy

### 2015-10-17 Rmd/carbon-bias.Rmd
17/10/2015 changes, see changelog

### Calculate weighted bias statistics
```{r, eval=FALSE}
# Helper functions to pass into data.table
# not used - switch on if quantiles needs
# bfn <- function(x, y) {
#   box_stats(x, weighted = TRUE, weight.opts = list("weights" = y))
# }
# bfna <- function(x, y) {
#   box_stats(abs(x), weighted = TRUE, weight.opts = list("weights" = y))
# }
wm <- function(x, w) stats::weighted.mean(x, w)
wma <- function(x, w) stats::weighted.mean(abs(x), w)

@@

# selection variables
nms1 <- c(colnames(ctabo), "wgt")
nms2 <- colnames(ctabo)
# bvals <- names(box_stats(sample(1:100, 200, replace = TRUE)))
bvals <- "mu"

@@

cb_stats$f25$geow[bvals == "m" & bin != "all", mean("forest")lapply(.SD, mean), 
                   .SDcols = LC]
cb_stats$f25$geow[bvals == "m", ]
cb_stats$f25$geow[bvals == "m" & bin != "all", lapply(.SD, mean), 
                  .SDcols = "forest"]

@@

### Plot means against scale, supplemental version 
```{r, eval=FALSE}
# cropland area only
a <- extract_stat0(LC, cb_stats, "all", "m")  # mean cropland only 
b <- cbind(V2 = "All", a[, lapply(.SD, mean), by = V1, .SDcols = lev_vec])
setcolorder(a, c(2:1, 3:ncol(a)))
mu <- rbind(a, b)  # bias

@@

### Main text version of mean carbon bias against scale

@@

cols <- c("red", "orange3", "green4", "blue")
lcnms <- c("SA LC", "GlobCover", "MODIS", "Geowiki")
pnms <- c("Forest", "Secondary", "Shrubland", "Grassland", "Sparse")
lw <- 1.5

yl <- range(mu[, 3:8, with = FALSE], mua[, 3:8, with = FALSE])
yl <- round(yl / 10) * 10
yax <- seq(yl[1], yl[2], 10)
xax <- seq(1, 6, 5 / (length(yax) - 1))

alph <- c(225, 40)
#Ccols <- brewer.pal(n = 7, name = "Greys")
LC2 <- c(LC[-grep("second|grass", LC)], "All")
# xax <- seq(0, 7, 6 / (length(yax) - 2)); length(xax)
x <- c(0, 3, 6, 9, 12, 15)
w <- 3 / 8
xo <- (cumsum(rep(w, 8)) - w / 2)[-c(2, 4, 6, 8)]
#x + xo[j] + o[k]
xa <- sapply(x, function(x) x + xo)
mutype <- c("mua", "mu")

o <- c(0, w)
pchs <- c("*", "+", "o", "-")
# cx <- c(1, 0.7, 0.6, 1)
cx <- c(2, 1.25, 1, 1)
g1 <- "grey90"
# pchShow()
# ctabo
xl <- c(-0.5, 18)
yl <- c(-60, 70)
shd <- c(4.5, 10.5, 16.5)

@@

```{r, eval=FALSE}
cols <- c("red", "orange3", "green4", "blue")
lcnms <- c("SA LC", "GlobCover", "MODIS", "Geowiki")
pnms <- c("Forest", "Secondary", "Shrubland", "Grassland", "Sparse")
lw <- 1.5

yl <- range(mund[, 3:8, with = FALSE], munda[, 3:8, with = FALSE])
yl <- round(yl / 10) * 10
yax <- seq(yl[1], yl[2], 10)
xax <- seq(1, 6, 5 / (length(yax) - 1))

@@

```{r, eval = FALSE, echo=FALSE}
# Version 1 of mean carbon bias against scale - probably for supplementals, if 
# retained
LC2 <- c(LC, "all")
pdf(full_path(p_fig, "carbon_veg_scale.pdf"), height = 7, width = 5)
par(mfrow = c(3, 2), mar = c(1, 0, 1, 1.25), mgp = c(1, 0.5, 0), tcl = -0.3,  
    oma = c(6, 4, 1, 0))
for(f in 1:length(LC2)) {
  plot(xax, yax, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
       ylab = "", xlab = "", 
       panel.first = grid(NA, length(yax), lwd = 1, lty = 1))
  #grid(NA, NULL, lwd = 1, lty = 1)
  mtext(side = 3, text = pnms[f], line = 0)
  if(f == 5) axis(1, at = 1:6, labels = c(1, fact))
  if(f %in% c(1, 3, 5)) axis(2, at = yax, labels = yax, las = 2)
  if(f %in% c(2, 4)) axis(2, at = yax, labels = rep("", length(yax)), las = 2)
  for(i in 1:4) {
    lines(1:6, mu[V1 == snms[i] & V2 == LC2[f], lev_vec, with = FALSE], 
          col = cols[i], lty = 2, lwd = lw)
  }
  for(i in 1:4) {
    lines(1:6, mua[V1 == snms[i] & V2 == LC2[f], lev_vec, with = FALSE], 
          col = cols[i], lty = 1, lwd = lw)
  }
}
# plot(xax, yax, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
#      ylab = "", xlab = "", 
#      panel.first = grid(NA, length(yax), lwd = 1, lty = 1))
# for(i in 1:4) {
#  lines(1:6, mu[V1 == snms[i], lev_vec, with = FALSE], col = cols[i], 
#        lty = 2, lwd = lw)
# }
# for(i in 1:4) {
#   lines(1:6, mua[V1 == snms[i], lev_vec, with = FALSE], col = cols[i],
#         lty = 1, lwd = lw)
# }
mtext(side = 3, text = "Vegetation mean", line = 0)
axis(1, at = 1:6, labels = c(1, fact))
axis(2, at = yax, labels = rep("", length(yax)), las = 2)
mtext(side = 1, text = "Resolution (km)", outer = TRUE, line = 1.5)
mtext(side = 2, text = "Bias/MAE (%)", outer = TRUE, line = 2)
par(xpd = NA)
x <- grconvertX(0.7, from = "ndc", to = "user")
y <- grconvertY(0.075, from = "ndc", to = "user")
legend(x = x, y = y, legend = c("Bias", "MAE"), lty = c(2, 1), 
       lwd = 2, bty = "n", cex = 1.2)
x <- grconvertX(0.1, from = "ndc", to = "user")
y <- grconvertY(0.11, from = "ndc", to = "user")
legend(x = x, y = y, legend = mcap, lty = 1, col = cols, lwd = 2, bty = "n",
       cex = 1.2)
dev.off()
```

### Supplementary mean bias tables
```{r, eval=FALSE}
# Statistics from non-croplands areas included in means, for supplementals
# mu0[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
# mu0a[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mu0s <- copy(rbind(cbind(Metric = "Bias", mu0), 
                   cbind(Metric = "MAE", mu0a)))
setnames(mu0s, c("V1", "V2", lev_vec), 
         c("Map", "Cover", paste(c(1, fact), "km")))
setkeyv(mu0s, c("Map", "Cover"))
for(i in 1:length(LC)) mu0s[Cover == LC[i], Cover := pnms[i]]
setkey(mu0s, "Map")
for(i in 1:length(snms)) mu0s[Map == snms[i], Map := mcap[i]]

@@

# still to do: tables for density independent biases
```

>>>>

### Calculate weighted bias statistics

#### Primary method

Weighted by __actual__ cropland percentage, and then, with aggregation, by number of pixels being aggregated.

```{r, eval=FALSE}
# Helper functions to pass into data.table
# not used - switch on if quantiles needs
# bfn <- function(x, y) {
#   box_stats(x, weighted = TRUE, weight.opts = list("weights" = y))
# }
# bfna <- function(x, y) {
#   box_stats(abs(x), weighted = TRUE, weight.opts = list("weights" = y))
# }

wm <- function(x, w) stats::weighted.mean(x, w)
wma <- function(x, w) stats::weighted.mean(abs(x), w)

# Bias
cb_statsw_mu <- rbindlist(lapply(lev_vec, function(x) {
  il <- rbindlist(lapply(snms, function(y) {
    ref <- gti_agg[[x]][[1]]
    awgts <- area_wgts[[x]][[1]]
    rerror <- c_pct_diff[[x]][[y]]
    bstats <- bias_statsw(ref, awgts, rerror, LC, wm, "Bias", rnd = 2, 
                          rweight = TRUE, aweight = TRUE, trim_wgt = TRUE)
    cbind("map" = y, bstats)
  }))
  # named_out(ol, snms)
  cbind("ol" = x, il)
}))

# calculate mean across cover types
cb_statsw_mu <- cbind(cb_statsw_mu, 
                      "All" = apply(cb_statsw_mu[, LC, with = FALSE], 1, mean))

# Accuracy
cb_statsw_mua <- rbindlist(lapply(lev_vec, function(x) { # x <- "f1"
  il <- rbindlist(lapply(snms, function(y) { # y <- "sa30"
    ref <- gti_agg[[x]][[1]]
    awgts <- area_wgts[[x]][[1]]
    rerror <- c_pct_diff[[x]][[y]]
    bstats <- bias_statsw(ref, awgts, rerror, LC, wma, "MAE", rnd = 2, 
                          rweight = TRUE, aweight = TRUE, trim_wgt = TRUE)
    cbind("map" = y, bstats)
  }))
  # named_out(ol, snms)
  cbind("ol" = x, il)
}))

# calculate mean across cover types
cb_statsw_mua <- cbind(cb_statsw_mua, 
                       "All" = apply(cb_statsw_mua[, LC, with=FALSE], 1, mean))
# rowMeans(as.data.frame(cb_statsw_mua[1, ])[, LC])

# check error stats - do they match alternate approaches?
for(i in c("f1", "f25", "f10")) { # i <- "f1"
  for(j in c("sa30", "modmu", "geow")) { # j <- "modmu"
    for(k in c("forest", "shrub", "sparse", "second")) {  # k <- "second"
      print(paste("cross-checking calculations in", i, j, k))
      ref <- gti_agg[[i]][[1]]
      awgts <- area_wgts[[i]][[1]]
      rerror <- c_pct_diff[[i]][[j]]
      a1 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu", 
                        aweight = FALSE)[, get(k)]
      a2 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu", 
                        rweight = FALSE, aweight = FALSE)[, get(k)]
      a3 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu")[, get(k)]
      c1 <- getValues(c_pct_diff[[i]][[j]][[k]])
      w1 <- getValues(gti_agg[[i]][[1]])
      w2 <- getValues(area_wgts[[i]][[1]])
      print("...non-area weighted mean matches?")
      print(a1 == round(weighted.mean(c1, w1, na.rm = TRUE), 2))
      print("...totally unweighted mean matches?")
      print(a2 == round(cellStats(rerror[[k]], mean), 2))
      print("...double weighted mean matches?")
      print(a3 == round(weighted.mean(c1, w1 * w2, na.rm = TRUE), 2))
    }
  }
}

````

#### Secondary methods

```{r, eval = TRUE}
# selection variables
nms1 <- c(colnames(ctabo), "wgt")
nms2 <- colnames(ctabo)
# bvals <- names(box_stats(sample(1:100, 200, replace = TRUE)))
bvals <- "mu"

@@

@@

cb_stats$f25$geow[bvals == "m" & bin != "all", lapply(.SD, mean), .SDcols = LC]
cb_stats$f25$geow[bvals == "m", ]
cb_stats$f25$geow[bvals == "m" & bin != "all", lapply(.SD, mean), 
                  .SDcols = "forest"]

@@

### Extract statistics for supplemental version 
```{r, eval=FALSE}
# cropland area only
a <- extract_stat0(LC, cb_stats, "all", "m")  # mean cropland only 
b <- cbind(V2 = "All", a[, lapply(.SD, mean), by = V1, .SDcols = lev_vec])
setcolorder(a, c(2:1, 3:ncol(a)))
mu <- rbind(a, b)  # bias

@@

### Plot mean carbon bias and accuracy against scale

#### Bias and accuracy weighted by agricultural area

```{r, eval = FALSE}
cols <- c("red", "orange3", "green4", "blue")
lcnms <- c("SA LC", "GlobCover", "MODIS", "Geowiki")
pnms <- c("Forest", "Secondary", "Shrubland", "Grassland", "Sparse")
lw <- 1.5

# yl <- range(cb_statsw_mu[, LC, with = FALSE], 
#             cb_statsw_mua[, LC, with = FALSE])
# yl <- round(yl / 10) * 10
yl <- c(-290, 290)
yax <- seq(yl[1], yl[2], 20)
xax <- seq(1, 6, 5 / (length(yax) - 1))

alph <- c(225, 40)
LC2 <- c(LC[-grep("second|grass", LC)], "All")
x <- c(0, 3, 6, 9, 12, 15)
w <- 3 / 8
xo <- (cumsum(rep(w, 8)) - w / 2)[-c(2, 4, 6, 8)]
xa <- sapply(x, function(x) x + xo)
mutype <- c("cb_statsw_mua", "cb_statsw_mu")

o <- c(0, w)
pchs <- c("*", "+", "o", "-")
cx <- c(2, 1.25, 1, 1)
g1 <- "grey90"

# ctabo
xl <- c(-0.5, 18)
# yl <- c(-200, 200)
shd <- c(4.5, 10.5, 16.5)

pdf(full_path(p_fig, "carbon_veg_scalew.pdf"), height = 7, width = 7)
par(mar = rep(1, 4), oma = c(2, 2, 0, 0), mgp = c(1, 0.5, 0), tcl = -0.3)
plot(xl, yl, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
     ylab = "", xlab = "")#,
for(i in shd) polyfunc2(x = i, y = yl, w = 3, col = g1, bcol = g1, lwd = 1)
abline(h = yax, v = NULL, col = "grey80", lty = 1)
polyfunc2(x = 8.75, y = yl, w = 18.5, col = "transparent", bcol = "black")
lines(c(-1, 18), c(0, 0), lwd = 2, col = "grey50")
for(i in 1:length(lev_vec)) { # i <- 1; j <- 1; k <- 1
  for(j in 1:length(snms)) {
    for(k in 1:length(mutype)) {
      dat <- get(mutype[k])[ol == lev_vec[i] & map == snms[j], LC2, with=FALSE]
      pcol <- makeTransparent(cols[j], alpha = alph[k])
      polyfunc2(xa[j, i] + o[k], range(dat), w = w, col = pcol, bcol = pcol)
      for(z in 1:length(LC2)) {
        lpfunc(x[i] + xo[j] + o[k], dat[, z, with = FALSE], col = "black", 
               size = cx[z], pch = pchs[z], type = "pt")
      }
    }
  }
}
axis(1, at = seq(1.5, 18.5, 3), labels = c(1, fact))
axis(2, at = yax, labels = yax, las = 2)
mtext(side = 1, text = "Resolution (km)", outer = TRUE, line = 0.5)
mtext(side = 2, text = "Bias/MAE (%)", outer = TRUE, line = 1)
legend(x = 12.4, y = -210, legend = lcnms, pch = 15, col = cols, adj = 0,
       pt.cex = 1.5, bty = "n", cex = 0.8, x.intersp = 0.5)
legend(x = 11.9, y = -210, legend = rep("", 4), pch = 15, adj = 0, 
       col = makeTransparent(cols, alpha = alph[2]), pt.cex = 1.5, bty = "n", 
       cex = 0.8)
text(x = 12.7, y = -212, labels = "MAE", srt = 45, adj = c(0, 0), cex = 0.8)
text(x = 12.2, y = -212, labels = "Bias", srt = 45, adj = c(0, 0), cex = 0.8)
legend(x = 12.1, y = 260, legend = c("Forest", "Shrubland", "Sparse", "Mean"), 
       pch = pchs, pt.cex = c(2, 1.5, 1.5, 2), bty = "n", cex = 0.8)
dev.off()

@@

# yl <- range(mu[, 3:8, with = FALSE], mua[, 3:8, with = FALSE])
# yl <- round(yl / 10) * 10
yax <- seq(yl[1], yl[2], 10)
xax <- seq(1, 6, 5 / (length(yax) - 1))

mutype <- c("mua", "mu")

xl <- c(-0.5, 18)
yl <- c(-60, 70)
shd <- c(4.5, 10.5, 16.5)

@@

```{r, eval=FALSE}
yl <- range(mund[, 3:8, with = FALSE], munda[, 3:8, with = FALSE])
yl <- round(yl / 10) * 10
yax <- seq(yl[1], yl[2], 10)
xax <- seq(1, 6, 5 / (length(yax) - 1))

@@

### Supplementary bias/accuracy tables
```{r, eval=FALSE}
# Statistics from cropland area-weighted measures, reshaped
cb_stats_s <- lapply(rev(mutype), function(i) {
  i0 <- do.call(rbind, lapply(snms, function(x) {
    i1 <- do.call(rbind, lapply(c(LC, "All"), function(y) {
      i2 <- do.call(cbind, lapply(lev_vec, function(z) {
        get(i)[ol == z & map == x, get(y)]
      }))
      cbind.data.frame(y, i2)
    }))
    i1 <- cbind.data.frame(x, i1)
    colnames(i1) <- c("Map", "Cover", lev_vec)
    data.table(i1)
  }))
})
names(cb_stats_s) <- c("Bias", "Accuracy")
muws <- copy(rbind(cbind(Metric = "Bias", cb_stats_s$Bias), 
                   cbind(Metric = "MAE", cb_stats_s$Accuracy)))
setnames(muws, lev_vec, paste(c(1, fact), "km"))
setkeyv(muws, c("Map", "Cover"))
for(i in 1:length(LC)) muws[Cover == LC[i], Cover := pnms[i]]
setkey(muws, "Map")
for(i in 1:length(snms)) muws[Map == snms[i], Map := mcap[i]]

# Statistics from non-croplands areas included in means, for supplementals
# mu0[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
# mu0a[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mu0s <- copy(rbind(cbind(Metric = "Bias", mu0), 
                   cbind(Metric = "MAE", mu0a)))
setnames(mu0s, c("V1", "V2", lev_vec), 
         c("Map", "Cover", paste(c(1, fact), "km")))
setkeyv(mu0s, c("Map", "Cover"))
for(i in 1:length(LC)) mu0s[Cover == LC[i], Cover := pnms[i]]
setkey(mu0s, "Map")
for(i in 1:length(snms)) mu0s[Map == snms[i], Map := mcap[i]]

@@

# still to do: tables for density independent biases

# Bind all three tables together
fulls <- rbind(cbind("Region" = "Density weighted", muws), 
               cbind("Region" = "Country", mu0s),
               cbind("Region" = "Agricultural", mus))

caption <- paste("Biases and mean absolute errors for each of the cropland", 
                 "maps across aggregation scales and each possible landcover", 
                 "type sharing the pixel with cropland. Three variants", 
                 "of the bias/accuracy values are provided, indicated by the:",
                 "Region column: 1) weighted by reference cropland density", 
                 "(Density weighted); 2) across the entire country (Country);",
                 "3) for agricultural areas only (Agricultural, i.e.", 
                 "$>$0.05\\% cropland).")
fulls_xtab <- xtable(fulls[order(Region, Metric, Cover)], digits = 1, 
                     caption = caption)
print(fulls_xtab, type = "latex", file = "paper/figures/C-bias-accuracy.tex", 
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE)

### 2015-10-17 Rmd/compare-landcover.Rmd
17/10/2015 changes, see changelog

# Overview
This section of the analysis calculates the differences between the GTI cropland percentages and those from the various landcover products. It draws from results generated by the [cropland pre-processing](cropland-preprocess.Rmd). (Note: html needed).

@@

caption <- paste("Biases and mean absolute errors (MAE) in cropland maps",
                 "relative to the 2011 reference map for each aggregation scale",
                 "calculated over the entire country, for the union of",
                 "agricultural regions (cropland $>$ 0), and as density", 
                 "independent means, wherein the mean bias/MAE values",
                 "for each of 20 cropland cover classes",
                 "(representing 5\\% increments of cover 0\\% to 100\\% defined",
                 "by the reference map) were calculated and then averaged.")
lcfout_xtab <- xtable(lcf_out11, digits = 1, caption = caption)
print(lcfout_xtab, type = "latex", file = "paper/figures/cropland2011-bias.tex", 
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE)

>>>>

# Overview
This section of the analysis calculates the differences between the GTI cropland percentages and those from the various landcover products. It draws from results generated by the [cropland pre-processing](cropland-preprocess.html). Bias statistics calculated here are primarily for the supplementals.

@@

caption <- paste("Biases and mean absolute errors (MAE) in cropland maps",
                 "relative to the 2011 reference map for each aggregation",
                 "scale calculated over the entire country, for the union of",
                 "agricultural regions (cropland $>$ 0), and as density", 
                 "independent means, wherein the mean bias/MAE values",
                 "for each of 20 cropland cover classes (representing",
                 "5\\% increments of cover 0\\% to 100\\% defined",
                 "by the reference map) were calculated and then averaged.")
lcfout_xtab <- xtable(lcf_out11, digits = 1, caption = caption)
print(lcfout_xtab, type = "latex", file = "paper/figures/cropland2011-bias.tex", 
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE)

### 2015-10-17 Rmd/cropland-bias.Rmd
17/10/2015 changes, see changelog

---
title: "Plotting cropland biases"
author: "Lyndon Estes"
date: "06 October 2014"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
    number_sections: true
---

# Plotting bias figures
# Spatial biases
## Datasets

@@

## Plots
Plot maps of biases at different resolutions, for publication output (and display here). To avoid the visual distortion of NA areas filled in by larger levels of aggregation, each aggregated difference must be disaggregated first and then masked before plotting.   
```{r, eval = FALSE}
namask <- raster(full_path(p_data, "namask.tif"))
# cellStats(namask, sum)
snms <- c("sa30", "globmu", "modmu", "geow")  # all lc data (no MOD/GC extremes)
lev <- c("f1", "f25", "f50", "f100")  # just show four levels

@@

wm <- function(x, w) stats::weighted.mean(x, w, na.rm = TRUE)
# wma <- function(x, w) stats::weighted.mean(abs(x), w)

@@

In relation to calculation method (across country, agricultural region only, or bin-wise (cropland density classes) mean.
```{r, eval = FALSE}
load(full_path(p_data, "lcf_out2011.rda"))
lcf <- data.table(lcf_out11)

>>>>

---
title: "Cropland Bias and Accuracy"
author: "Lyndon Estes"
date: "06 October 2014"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
    number_sections: true
---

# Overview

The following provide further analyses and plots of bias and accuracy metrics calculated from spatial error maps created in [compare-landcover](compare-landcover.html) (which includes some supplementary metrics),

# Spatial biases
## Datasets

@@

## Plots
Plot maps of biases at different resolutions, for publication output (and display here). To avoid the visual distortion of NA areas filled in by larger levels of aggregation, each aggregated difference must be disaggregated first and masked before plotting.   
```{r, ethen val = FALSE}
namask <- raster(full_path(p_data, "namask.tif"))
# cellStats(namask, sum)
snms <- c("sa30", "globmu", "modmu", "geow")  # all lc data (no MOD/GC extremes)
lev <- c("f1", "f25", "f50", "f100")  # just show four levels

@@

wm <- function(x, w) stats::weighted.mean(x, w, na.rm = TRUE)
wma <- function(x, w) stats::weighted.mean(abs(x), w)

@@

## Primary method

Weighted by __actual__ cropland percentage, and then, with aggregation, by number of pixels being aggregated.

```{r, eval = FALSE}
# Create weights maks
fact <- c(5, 10, 25, 50, 100)
namask <- raster(full_path(p_data, "namask.tif"))  # NA mask
# cellStats(!is.na(gti$g2011), sum)
# cellStats(namask, sum)

namask2 <- !is.na(namask)
awgts <- aggregate_rast_list(fact, list(namask2), fun = sum)
awgts <- lapply(awgts, function(x) x[[1]])

# Subset difference grids, for 2011
snms <- c("sa30", "globmu", "modmu", "geow")
err2011[[1]]
err2011 <- lapply(lev, function(x) {
  sapply(dlist_act[snms], function(y) list(y[[x]]$g2011))
})
names(err2011) <- lev

gti_agg <- aggregate_rast_list(fact, gti)  # GTI rasters
gti_agg11 <- lapply(gti_agg, function(x) x$g2011)

# calculate bias/MAE for data
a <- bias_statsw_list(gti_agg11, awgts, err2011, snms, wm, "mu")
b <- bias_statsw_list(gti_agg11, awgts, err2011, snms, wma, "mua")
bacc2011 <- rbind(a, b)

# check error stats - do they match alternate approaches?
for(i in c("f1", "f25", "f10")) {
  for(j in c("sa30", "modmu", "geow")) { 
    print(paste("cross-checking calculations in", i, j))
    a1 <- bias_statsw(gti_agg11[[i]], awgts[[i]], err2011[[i]], snms, wm, 
                      "mu", aweight = FALSE)[, j, with = FALSE]
    a2 <- bias_statsw(gti_agg11[[i]], awgts[[i]], err2011[[i]], snms, wm, 
                      "mu", rweight = FALSE, aweight = FALSE)[,j, with=FALSE]
    a3 <- bias_statsw(gti_agg11[[i]], awgts[[i]], err2011[[i]], snms, wm, 
                      "mu")[, j, with = FALSE]
    c1 <- getValues(err2011[[i]][[j]])
    w1 <- getValues(gti_agg11[[i]])
    w2 <- getValues(awgts[[i]])
    print("non-area weighted mean matches?")
    print(a1 == round(weighted.mean(c1, w1, na.rm = TRUE), 2))
    print("totally unweighted mean matches?")
    print(a2 == round(cellStats(err2011[[i]][[j]], mean), 2))
    print("double weighted mean matches?")
    print(a3 == round(weighted.mean(c1, w1 * w2, na.rm = TRUE), 2))
  }
}

# Subset difference grids, for 2007
snms <- c("sa30", "globmu", "modmu", "geow")
err2007 <- lapply(lev, function(x) {
  sapply(dlist_act[snms], function(y) list(y[[x]]$g2007))
})
names(err2007) <- lev
gti_agg07 <- lapply(gti_agg, function(x) x$g2007)

a <- bias_statsw_list(gti_agg07, awgts, err2007, snms, wm, "mu")
b <- bias_statsw_list(gti_agg07, awgts, err2007, snms, wma, "mua")
bacc2007 <- rbind(a, b)

fact <- c(1, 5, 10, 25, 50, 100)
alph <- c(225, 40)
x <- c(0, 3, 6, 9, 12, 15)
w <- 3 / 8
xo <- (cumsum(rep(w, 8)) - w / 2)[-c(2, 4, 6, 8)]
o <- c(0, w)
xa <- sapply(x, function(x) x + xo)
cx <- c(1.25, 1, 1)
g1 <- "grey90"
reg <- c("Country", "Agricultural", "Density independent")
lcnms <- c("SA-LC", "GlobCover", "MODIS", "GeoWiki")
mutype <- c("mua", "mu")
# svec <- paste(gsub("f", "", bacc2011[stnm == "mu", ol]), "km")
svec <- bacc2011[stnm == "mu", ol]
xl <- c(-0.5, 18)
yl <- c(-30, 50)
shd <- c(4.5, 10.5, 16.5)
cols <- c("red", "orange3", "green4", "blue")
colnms <- snms
pchs <- c("+", "o", "x")
yax <- seq(yl[1], yl[2], 5)
xax <- seq(1, 6, 5 / (length(yax) - 1))

pdf(full_path(p_fig, "cropland_bias_mainw.pdf"), height = 7, width = 7)
par(mar = rep(1, 4), oma = c(2, 2, 0, 0), mgp = c(1, 0.5, 0), tcl = -0.3)
plot(xl, yl, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
     ylab = "", xlab = "")#,
for(i in shd) polyfunc2(x = i, y = yl, w = 3, col = g1, bcol = g1, lwd = 1)
abline(h = yax, v = NULL, col = "grey80", lty = 1)
polyfunc2(x = 8.75, y = yl, w = 18.5, col = "transparent", bcol = "black")
lines(c(-1, 18), c(0, 0), lwd = 2, col = "grey80")
# i <- 1; j <- 1; k <- 1
for(i in 1:length(svec)) {
  lv <- svec[i]
  for(j in 1:length(snms)) {
    # pchs1 <- pchs
    nm <- snms[j]
    for(k in 1:length(mutype)) {
      #dat <- get(mutype[k])[V1 == snms[j] & V2 %in% LC2, get(lev_vec[i])]
      #dat <- lcf[Metric == mutype[k] & Map == nm, lv, with = FALSE]
      dat <- bacc2011[ol == lv & stnm == mutype[k], nm, with = FALSE][[1]]
      pcol <- makeTransparent(cols[j], alpha = alph[k])
      #polyfunc2(xa[j, i] + o[k], range(dat), w = w, col = pcol, bcol = pcol)
      polyfunc2(xa[j, i] + o[k], c(0, dat), w = w, col = pcol, bcol = pcol)
      # for(z in 1:length(reg)) {
        # lpfunc(x[i] + xo[j] + o[k], dat[z], col = "black", size = cx[z], 
               # pch = pchs[z], type = "pt")
      # }
    }
  }
}
axis(1, at = seq(1.5, 18.5, 3), labels = fact)
axis(2, at = yax, labels = yax, las = 2)
mtext(side = 1, text = "Resolution (km)", outer = TRUE, line = 0.5)
mtext(side = 2, text = "Bias/MAE (%)", outer = TRUE, line = 1)
legend(x = 12.4, y = -19.9, legend = lcnms, pch = 15, col = cols, adj = 0,
       pt.cex = 1.5, bty = "n", cex = 0.8, x.intersp = 0.5)
legend(x = 11.9, y = -19.9, legend = rep("", 4), pch = 15, adj = 0, 
       col = makeTransparent(cols, alpha = alph[2]), pt.cex = 1.5, bty = "n", 
       cex = 0.8)
text(x = 12.7, y = -20.5, labels = "MAE", srt = 45, adj = c(0, 0), cex= 0.8)
text(x = 12.2, y = -20.5, labels = "Bias", srt = 45, adj = c(0, 0), cex = 0.8)
# legend(x = 12.1, y = 40, 
#        legend = c("Country", "Agricultural", "Density independent"), pch = pchs, 
#        pt.cex = c(1.5, 1.5), bty = "n", cex = 0.8)
dev.off()

fact <- c(1, 5, 10, 25, 50, 100)
alph <- c(225, 40)
x <- c(0, 3, 6, 9, 12, 15)
w <- 3 / 8
xo <- (cumsum(rep(w, 8)) - w / 2)[-c(2, 4, 6, 8)]
o <- c(0, w)
xa <- sapply(x, function(x) x + xo)
cx <- c(1.25, 1, 1)
g1 <- "grey90"
reg <- c("Country", "Agricultural", "Density independent")
lcnms <- c("SA-LC", "GlobCover", "MODIS", "GeoWiki")
mutype <- c("MAE", "Bias")
svec <- paste(gsub("f", "", bacc2011[stnm == "mu", ol]), "km")
xl <- c(-0.5, 18)
yl <- c(-40, 40)
shd <- c(4.5, 10.5, 16.5)
cols <- c("red", "orange3", "green4", "blue")
colnms <- snms
pchs <- c("+", "o", "x")
yax <- seq(yl[1], yl[2], 5)
xax <- seq(1, 6, 5 / (length(yax) - 1))

pdf(full_path(p_fig, "cropland_bias_main.pdf"), height = 7, width = 7)
par(mar = rep(1, 4), oma = c(2, 2, 0, 0), mgp = c(1, 0.5, 0), tcl = -0.3)
plot(xl, yl, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
     ylab = "", xlab = "")#,
for(i in shd) polyfunc2(x = i, y = yl, w = 3, col = g1, bcol = g1, lwd = 1)
abline(h = yax, v = NULL, col = "grey80", lty = 1)
polyfunc2(x = 8.75, y = yl, w = 18.5, col = "transparent", bcol = "black")
lines(c(-1, 18), c(0, 0), lwd = 2, col = "grey80")
# i <- 1; j <- 1; k <- 1
for(i in 1:length(svec)) {
  lv <- colnms[i]
  for(j in 1:length(snms)) {
    pchs1 <- pchs
    nm <- lcnms[j]
    for(k in 1:length(mutype)) {
      #dat <- get(mutype[k])[V1 == snms[j] & V2 %in% LC2, get(lev_vec[i])]
      dat <- lcf[Metric == mutype[k] & Map == nm, lv, with = FALSE]
      pcol <- makeTransparent(cols[j], alpha = alph[k])
      polyfunc2(xa[j, i] + o[k], range(dat), w = w, col = pcol, bcol = pcol)
      for(z in 1:length(reg)) {
        lpfunc(x[i] + xo[j] + o[k], dat[z], col = "black", size = cx[z], 
               pch = pchs[z], type = "pt")
      }
    }
  }
}

axis(1, at = seq(1.5, 18.5, 3), labels = fact)
axis(2, at = yax, labels = yax, las = 2)
mtext(side = 1, text = "Resolution (km)", outer = TRUE, line = 0.5)
mtext(side = 2, text = "Bias/MAE (%)", outer = TRUE, line = 1)
legend(x = 12.4, y = -19.9, legend = lcnms, pch = 15, col = cols, adj = 0,
       pt.cex = 1.5, bty = "n", cex = 0.8, x.intersp = 0.5)
legend(x = 11.9, y = -19.9, legend = rep("", 4), pch = 15, adj = 0, 
       col = makeTransparent(cols, alpha = alph[2]), pt.cex = 1.5, bty = "n", 
       cex = 0.8)
text(x = 12.7, y = -20.5, labels = "MAE", srt = 45, adj = c(0, 0), cex= 0.8)
text(x = 12.2, y = -20.5, labels = "Bias", srt = 45, adj = c(0, 0), cex = 0.8)
legend(x = 12.1, y = 40, 
       legend = c("Country", "Agricultural", "Density independent"), pch = pchs, 
       pt.cex = c(1.5, 1.5), bty = "n", cex = 0.8)
dev.off()
```

## Other calculations methods

Across country, agricultural region only, or bin-wise (cropland density classes) mean.
```{r, eval = FALSE}
load(full_path(p_data, "lcf_out2011.rda"))
lcf <- data.table(lcf_out11)
